---
title: "R Notebook"
output: html_notebook
---

# Introduction to ggplot2 Homework

## Question 1
### Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
library(tidyverse)
library(CodeClanData)


view(backpack)
glimpse(backpack)
```

## Question 2
### What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack, aes(x = backpack_weight)) +
  geom_histogram(binwidth = 5, 
                 fill = "steelblue", 
                 colour = "grey") +
  labs(title = "Student Backpack Weight Distribution",
       x = "\nBackpack Weight",
       y = "\nNumber of Backpacks") +
  scale_x_continuous(n.breaks = 10)
  theme_minimal()
  
```
> histogram of the distribution of the weights carried by students
> more than half of the students carry a bag between 5 and 15 kgs(?)


## Question 3
### Are there differences in backpack weight between sex?

```{r}
backpack_weight_by_sex <- backpack %>% 
  group_by(sex) %>% 
  summarise(avg_backpack_weight = mean(backpack_weight)) 

ggplot(backpack_weight_by_sex, aes(x = sex, 
                                   y = avg_backpack_weight,
                                   fill = sex)) +
  geom_col() +
  labs(title = "Average Backpack Weight by Sex",
       x = "Sex",
       y = "Average Backpack Weight") +
  theme_light()
 
# I want to change the size of my plot but have no idea how to  
```
 > shows the average backpack weight carried by male and female students
 > males on average carry heavier backpacks, but not by much
 
## Question 4
### What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight, colour = "orange") +
  geom_point(show.legend = FALSE) +
  geom_smooth(method = lm) +
  labs(title = "Body weight vs Backpack Weight",
       x = "Body Weight",
       y = "Backpack Weight") +
  theme_light()
```
> Shows the relationship between body weight and backpack weight, seems like there is only a minimal (if any) relationship between the two variables

## Question 5
### Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight, colour = sex) +
  geom_point(show.legend = FALSE) +
  geom_smooth(method = lm) +
  labs(title = "Body weight vs Backpack Weight",
       x = "Body Weight",
       y = "Backpack Weight") +
  facet_wrap(~ sex) +
  theme_light()
```

> perhaps more of a relationship in females


