---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
```

1. Loading data and checking

```{r}
dim(drinks_content)
```

```{r}
names(drinks_content)
```

```{r}
head(drinks_content)
```

```{r}
glimpse(drinks_content)
```

2. Selecting columns to keep

```{r}
calorie_data <- select(drinks_content, Beverage_category, Beverage, Beverage_prep, Calories)
dim(calorie_data)
```

```{r}
drop_na(calorie_data, Beverage_category, Beverage, Beverage_prep, Calories)
```

3. Create a new column called calorie_diff

```{r}
mutate(calorie_data, 
       Calorie_diff = Calories - 135)
```

4. Summaries the mean number of calories in each beverage_category. Which 3 categories of drinks have the most calories? Which 3 drinks have the least? 

```{r}
grouped_beverage <- group_by(calorie_data, Beverage_category)
grouped_beverage
```
```{r}
arrange(summarise(grouped_beverage, mean_calories = mean(Calories)), desc(mean_calories))
```
Top 3 = "Smoothies", "Frappuccino Blended Coffee", "Signature Espresso Drinks"
Bottom 3 = "Classic Espresso Drinks", "Shaken Iced Beverages", "Coffee"

5. What is the average number of calories in each Beverage_prep type?

```{r}
grouped_by_prep <- group_by(calorie_data, Beverage_prep)
grouped_by_prep_mean <- summarise(grouped_by_prep, mean_calorie_prep = mean(Calories))
grouped_by_prep_mean
```

6. Which beverage_prep type contains more than the average calories of all drinks?

```{r}
average_calorie <- pull(summarise(calorie_data,
                                  mean(Calories)))

filter(grouped_by_prep_mean, mean_calorie_prep > average_calorie)
```

7. Which is the best type of coffee drink to get if you're worried about consuming too many calories?

```{r}
arrange(calorie_data, Calories)
```
Short Brewed Coffee
