---
title: "R Notebook"
output: html_notebook
---

# Decision Trees Homework

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(GGally)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

```{r}
skimr::skim(titanic_set)
```

```{r}
summary(titanic_set)
```

## 1. Cleaning Data

```{r}
titanic_clean <- titanic_set %>% 
  mutate(age_status = if_else(age >= 16, "adult", "child")) %>% 
  mutate(age_status = as_factor(age_status),
         sex = as_factor(sex),
         port_embarked = as_factor(embarked),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
         survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes"))) %>% 
  select(-c(...1, passenger_id, name, ticket, fare, cabin, age, survived, pclass, embarked)) %>% 
  na.omit()
```

## 2. Plotting data

```{r, message = FALSE}
titanic_clean %>% 
  ggpairs(aes(colour = survived_flag, alpha = 0.5))
```
Sex, class, age all look like possibly good predictors


```{r}
titanic_clean %>% 
  count(sex)
```

## 3. Split test and train data

```{r}
library(splitstackshape)

stratified_samples <- stratified(titanic_clean, 
           group = c("sex", "age_status", "class"),
           size =  0.8,
           bothSets = TRUE)

titanic_train <- stratified_samples$SAMP1

titanic_test <- stratified_samples$SAMP2
```

```{r}
titanic_train %>% 
  janitor::tabyl(survived_flag)

titanic_test %>% 
  janitor::tabyl(survived_flag)
```


## Create a decision tree

```{r}
titanic_fit <- rpart(
  formula = survived_flag ~.,
  data = titanic_train,
  method = "class"
)

rpart.plot(titanic_fit,
           yesno = 2,
           fallen.leaves = TRUE,
           faclen = 6,
           digits = 4,
           type = 4,
           extra = 101)
```

```{r}
rpart.rules(titanic_fit, cover = TRUE, style = "tallw")
```

## 5. Interpretation 


Sex and class are the most important predictors, along with sib_sp and age_status. 

Adult men in lower or middle class have the highest chance of survival (I assume, however, this is because there are probably more males in the data/on the titanic). Next are middle or upper class women (adult/child). Then upperclass men. Those with the lowest probability of survial are lower or middle class children with more than 3 siblings (assuming not spouses...), with just a 2% chance. 


## 6. Predictions and confusion matrix

```{r}
library(modelr)

titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")

titanic_test_pred %>% 
  select(sex, sib_sp, age_status, class, survived_flag, pred)
  
```

```{r}
library(yardstick)

conf_mat <- titanic_test_pred %>% 
  conf_mat(truth = survived_flag, estimate = pred)

conf_mat
```

FPs = 6
FNs = 16

```{r}
accuracy <- titanic_test_pred %>% 
  accuracy(truth = survived_flag, estimate = pred)
```

```{r}
titanic_test_pred %>% 
  sensitivity(truth = survived_flag, estimate = pred)
  
titanic_test_pred %>%   
  specificity(truth = survived_flag, estimate = pred)
```

