---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
```

#### Question 1.

Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable n

```{r}
code_clan_tweets <- read_csv("data/code_clan_tweets.csv")
```
No of rows
```{r}
code_clan_tweets %>% 
  nrow()
```

No of columns
```{r}
code_clan_tweets %>% 
  ncol()
```

```{r}
code_clan_tweets %>% 
  names()
```

```{r}
glimpse(code_clan_tweets)
view(code_clan_tweets)
```

#### Question 2.

Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
code_clan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(sum(favorite_count))
```

####Question 3.

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
code_clan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean(retweet_count))
```
#### Question 4.

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
code_clan_tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_favourite_count = sum(favorite_count)) %>% 
  arrange(desc(total_favourite_count))
  
```

#### Question 5.

Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
code_clan_tweets %>% 
  summarise(mean_character_count = mean(nchar(text))) 

code_clan_tweets %>% 
  summarise(mean_display_text_width = mean(display_text_width))
  
```

#### Question 6.

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")
```

```{r}
view(code_clan_info)
```

```{r}
names(code_clan_info)
```

```{r}
code_clan_joined <- code_clan_tweets %>% 
  inner_join(code_clan_info, by = "tweet_id")

#Answer gives a left join
#Gives same result - because there's a 1-1 relationship between the tibbles.

code_clan_tweets %>% 
  left_join(code_clan_info, by = "tweet_id")
```

#### Question 7.

From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and convert the hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}
#codeclan_hashtags <- code_clan_joined %>% 
  #mutate(text = str_to_lower(text)) %>% 
  #filter(text %in% c("#")) %>% 
  #select(tweet_id) 
# I was making it more complicated by not realising there was a hashtags column

#Answer
codeclan_hashtags <- code_clan_joined%>% 
  select(tweet_id, hashtags) %>%
  mutate(lowcase_hashtag = str_to_lower(hashtags)) %>%
  select(-hashtags) %>%
  drop_na(lowcase_hashtag)

codeclan_hashtags
  
```

## Extension

#### Question 10.

Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.

```{r}
code_clan_tweets %>% 
  select(text) %>% 
  str_extract_all("@[A-Za-z0-9_]+")

#I had the plus in the wrong position 
```

#### Question 9.

Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.

```{r}
codeclan_hashtags %>% 
  select(text) %>% 
  str_count("edinburgh")
```
```{r}
#Answer Given
code_clan_tweets %>%
  mutate(lowcase_tweets = str_to_lower(text)) %>%
  filter(str_detect(lowcase_tweets, "edinburgh")) %>%
  summarise(count = n())

```

#### Question 8. 

Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(.

I didn't attempt this

```{r}
#Answer given 

hashtags_multiple <- codeclan_hashtags %>% 
  mutate(first_letters = str_sub(lowcase_hashtag, 1, 2)) %>%
  filter(str_detect(first_letters, "c\\("))

hashtags_multiple
```

