---
title: "R Notebook"
output: html_notebook
---
# Distributions Homework


```{r}
library(tidyverse)
library(janitor)
```

```{r}
mobile_phones <- read_csv("data/20190928-items.csv") %>% 
  clean_names()
```
## Question 2.
### Find the brand with the highest numbers of phones in the dataset.

```{r}
mobile_phones %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  slice_max(count)

```
## Question 3.
### For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?


```{r}
samsung <- mobile_phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    mean = mean(rating),
    sd = sd(rating)
  )
 


mobile_phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung$mean,
      sd = samsung$sd
    ),
    col = "red"
  )
```
> seems somewhat normally distributed
> the data appears to be left-skewed

## Question 4.
### We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}
# 1 sd 
samsung_ratings <- mobile_phones %>% 
  filter(brand == "Samsung")

samsung_ratings %>% 
  filter(rating >= samsung$mean - samsung$sd) %>% 
  filter(rating <= samsung$mean + samsung$sd) %>% 
  summarise(prop_1sd = n()/nrow(samsung_ratings))
```
```{r}
# 2 sd
samsung_ratings %>% 
  filter(rating >= samsung$mean - (2 * samsung$sd)) %>% 
  filter(rating <= samsung$mean + (2 * samsung$sd)) %>% 
  summarise(prop_1sd = n()/nrow(samsung_ratings))

```

```{r}
# 3 sd

samsung_ratings %>% 
  filter(rating >= samsung$mean - (3 * samsung$sd)) %>% 
  filter(rating <= samsung$mean + (3 * samsung$sd)) %>% 
  summarise(prop_1sd = n()/nrow(samsung_ratings))
```
> would expect, if normally distributed, that 99% of the values would be within 3 sd of the mean
> as there's about 98% of the data values within 3sd then it seems like the data is left skewed and not normally distributed

> too few values between 1 & 2 sd away from mean