---
title: "R Notebook"
output: html_notebook
---
# Simple Linear Regression Homework


```{r}
library(tidyverse)
library(janitor)
library(broom)
```


## MVP
### 1

```{r}
# Load data

project <- read_csv("data/project_management.csv") %>% 
  clean_names()

```
* Plot the data

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```

* Calculate the correlation coefficient

```{r}
project %>% 
  summarise(cor(estimated_length, actual_length))
```
The correlation coefficent is between 0.8 and 0.99 and therefore can be considered "very strong" on Evans' scale of magnitude.


* Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}
model <- lm(formula = actual_length ~ estimated_length,
            data = project)

summary(model)
model %>% glance()
```

* Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

> For every 1 unit that estimated_length changes actual_length changes by 1.2235
> The r^2 value states that 64.7% of the variation in actual_length can be explained by variation in estimated_length. 

* Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).

```{r}
library(ggfortify)

autoplot(model)
```

> meh, p-value is statistically significant....but....
> looks like there's some sort of pattern to the variation in the data and the line on the first plot hovers round 0 then drops at the end
> outlier really pulling the data