---
title: "R Notebook"
output: html_notebook
---

# Confidence Interval Homework

## Q1
### Load the data again, clean_names(), and re-familiarise yourself with it

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()

glimpse(ames)
```

## Q2
### Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>% 
  ggplot(aes(x = lot_area)) + 
  geom_histogram(binwidth = 1000)
```

> roughly normal...maybe... very right skewed

## Q3
### Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_sample <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrap_sample %>% 
  ggplot(aes(x = stat)) +
  geom_histogram()
```


## Q4
### Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
ci_95 <- bootstrap_sample %>% 
  get_ci(level = 0.95, type = "percentile")

bootstrap_sample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_95)

```


## Q5
### You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99%
 CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95%
 CI? Does that make sense?
 
```{r}
ci_99 <- bootstrap_sample %>% 
  get_ci(level = 0.99, type = "percentile")

bootstrap_sample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_99)
```
 
 > they're wider (as I suspected) because they're capturing a higher percentage of the data points
 
 ## Q6
 ### Calculate the point estimate of the mean(lot_area)
 
```{r}
mean_bootstrap_sample <- bootstrap_sample %>% 
  summarise(mean = mean(stat))

mean_bootstrap_sample
```
 
# 2 Extension


## Task 1.
### Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting]. 

```{r}
before_1920 <- ames %>% 
  mutate(before_1920 = if_else(
    year_built < 1920, "Yes", "No"
  ), .after = year_built) 

p_est <- before_1920 %>% 
  summarise(prop_before_1920 = sum(before_1920 == "Yes")/n())

```
200 reps
```{r}
bootstrap_prop_200 <- before_1920 %>% 
  specify(response = before_1920, success = "Yes") %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_200 <- bootstrap_prop_200 %>% 
  get_ci(level = 0.95, type = "percentile")

ci_95_200

p_est_200 <- bootstrap_prop_200 %>% 
  summarise(mean = mean(stat))

p_est_200
```

500 reps
```{r}
bootstrap_prop_500 <- before_1920 %>% 
  specify(response = before_1920, success = "Yes") %>% 
  generate(reps = 500, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_500 <- bootstrap_prop_500 %>% 
  get_ci(level = 0.95, type = "percentile")

ci_95_500

p_est_500 <- bootstrap_prop_500 %>% 
  summarise(mean = mean(stat))

p_est_500
```

1000 reps

```{r}
bootstrap_prop_1000 <- before_1920 %>% 
  specify(response = before_1920, success = "Yes") %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1000 <- bootstrap_prop_1000 %>% 
  get_ci(level = 0.95, type = "percentile")

ci_95_1000

p_est_1000 <- bootstrap_prop_1000 %>% 
  summarise(mean = mean(stat))

p_est_1000
```

2000 reps

```{r}
bootstrap_prop_2000 <- before_1920 %>% 
  specify(response = before_1920, success = "Yes") %>% 
  generate(reps = 2000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_2000 <- bootstrap_prop_2000 %>% 
  get_ci(level = 0.95, type = "percentile")

ci_95_2000

p_est_2000 <- bootstrap_prop_2000 %>% 
  summarise(mean = mean(stat))

p_est_2000
```

5000 reps

```{r}
bootstrap_prop_5000 <- before_1920 %>% 
  specify(response = before_1920, success = "Yes") %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_5000 <- bootstrap_prop_5000 %>% 
  get_ci(level = 0.95, type = "percentile")

ci_95_5000

p_est_5000 <- bootstrap_prop_5000 %>% 
  summarise(mean = mean(stat))

p_est_5000
```

> they're getting more concentrated towards the centre (I think)