---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
movie_data <- read_csv("tmdb_5000_movies.csv")

view(movie_data)
```

```{r}
glimpse(movie_data)
```

1. Could group by genre/status. Create a profit column that takes revenue away from budget. There's some NAs to deal with & some formatting issues with some character columns. 
REMEMBER: to check for NAs
```{r}
sum(is.na(movie_data))
```


2. 

```{r}
movies_selected <- movie_data %>%
  select(title, runtime, budget)

movies_selected
```

3.

```{r}
movies_selected %>%
  summarise(
    na_count_title = sum(is.na(title)),
    na_count_runtime = sum(is.na(runtime)),
    na_count_budget = sum(is.na(budget))
  )
```

4. 


```{r}
movies_runtime <- movies_selected %>%
  mutate(runtime = na_if(runtime, 0))

movies_runtime %>%
  summarise(na_count_runtime = sum(is.na(runtime)))
```

5. 

```{r}
movies_imputed <- movies_runtime %>%
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed %>%
  filter(is.na(runtime))

#Answer: 
movies_imputed %>% 
  summarise(count = sum(is.na(runtime)))
```

6. 

```{r}
movies_imputed %>%
  slice_min(runtime, n = 10)
```
```{r}
movies_imputed %>%
  slice_max(runtime, n = 10)
```

7. 

```{r}
movies_imputed %>% 
  mutate(
    budget = if_else(budget < 100, median(budget), budget))
#I didn't add na.rm = TRUE? but the answer doesn't either...
```

Extension
1. 

```{r}
movies_imputed %>% 
  mutate(budget_type = case_when(
    budget < 12e6 ~ "Small budget",
    budget >= 12e6 & budget < 40e6 ~ "Medium budget", 
    budget >= 40e6 ~ "Big budget"
    )
  )


```

```{r}
#Answer:
movie_budgets <- movies_imputed %>%
  mutate(
    budget_type = case_when(
      budget < 12e6 ~ "Small budget",
      budget < 40e6 ~ "Medium budget",
      budget >= 40e6 ~ "Big budget"
      )
    )

movie_budgets
```

2. 
Take the original dataset with all the variables. Using across and where, summarise the number of missing values, first across all columns of type character, and then across all columns of type numeric.


```{r}
#Answer:

movie_data %>%
  summarise(across(where(is.numeric), ~ sum(is.na(.x))))

```
```{r}
movie_data %>%
  summarise(across(where(is.character), ~sum(is.na(.x))))
```

