---
title: "R Notebook"
output: html_notebook
---

# Probability Homework

```{r}
library(prob)
library(gtools)
library(tidyverse)
library(janitor)
```


## 1.1 The Titanic

```{r}
titanic <- read_csv("data/titanic.csv")
```
```{r}
head(titanic)
```
```{r}
view(titanic)
```

```{r}
titanic %>% 
  distinct(class)
```

New logical column for crew 

```{r}
titanic <- titanic %>% 
  mutate(crew = if_else(
    class %in% c("1st", "2nd", "3rd"), FALSE, TRUE
  ))

#titanic %>% 
  #filter(crew == TRUE)
```

P(survived|crew) = P(survived & crew) / P(crew)

```{r}
# P(crew)

s_titanic <- nrow(titanic)
s_titanic

s_titanic_crew = titanic %>% 
  filter(crew == TRUE) %>% 
  summarise(num_crew = n())
s_titanic_crew

p_crew <- s_titanic_crew / s_titanic
p_crew
```

```{r}
# P(survived & crew)

p_survived_crew <- titanic %>% 
  filter(survived == "yes" & crew == TRUE) %>% 
  summarise(prob = n() / s_titanic)
```


```{r}
# P(survived|crew) = P(survived & crew) / P(crew)

p_survived_crew <- p_survived_crew / p_crew
```

P(survived|passenger) = P(survived & passenger) / p(passenger)

```{r}
titanic_table <- titanic %>% 
  tabyl(crew, survived)

titanic_table <- titanic_table %>% 
  adorn_totals(where = c("row", "col")) 
 
titanic_table <- titanic_table %>% 
  adorn_percentages(denominator = "all") %>%
  adorn_title()
```

```{r}
p_survived_passenger <- 0.226551880380607 / 0.596737652922519
```

# 1.2 

## Question 1
### If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
s_1_dice <- rolldie(1)

s_less_than_5 <- s_1_dice %>% filter(X1 < 5)

p_less_than_5 <- nrow(s_less_than_5) / nrow(s_1_dice)
p_less_than_5
```

## Question 2
### How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
s_3_die <- rolldie(3) %>% 
  summarise(s = n())

s_3_die
```

## Question 3.
### In an experiment where we roll four dice:
> how many outcomes are in the event where the total of the four dice equals 5, 6 or 7?

```{r}
s_4_die <- rolldie(4)

s_5_6_7 <- s_4_die %>% 
  mutate(total = rowSums(.)) %>% 
  filter(total == 5 | total == 6 | total == 7)

nrow(s_5_6_7)
```

> what is the probability of this event?

```{r}
p_5_6_7 <- nrow(s_5_6_7) / nrow(s_4_die)
p_5_6_7
```

> what assumptions do we apply in answering part ii?

That common outcomes aren't counted twice/4 times etc...


## Question 6.
### If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades? 

```{r}
s_cards <- cards() %>% 
  mutate(black_card = if_else(
    suit %in% c("Spade", "Club"), TRUE, FALSE
  )) 
  
s_spades <- s_cards %>% 
  filter(suit == "Spade")

p_spades <- nrow(s_spades) / nrow(s_cards)
p_spades

s_spades_and_black <- s_cards %>% 
  filter(suit == "Spade" & black_card == TRUE)

p_spades_and_black <- nrow(s_spades_and_black) / nrow(s_cards)

# P(spades|black) 

p_black_spades <- p_spades_and_black * p_spades
p_black_spades
```

