---
title: "R Notebook"
output: html_notebook
---

# Hypothesis Testing Homework

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

# 1.1 Practical


## Q1
### Explore the dataset and familiarise yourself with it.

```{r}
summary(msleep)
glimpse(msleep)

msleep %>% 
  summarise(count_na = sum(is.na(sleep_total)))
```
```{r}
view(msleep)
```


## Q2
### Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

H0: the mean of sleep_total = 7 hours a night
H1: the mean of sleep_total ≠ 7 hours a night
sig = 0.05
One-sample Hypothesis Test

```{r}
sleep_mean <- msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

sleep_mean
```
```{r}
null_distribution_mean <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(10000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution_mean %>% 
  visualise(30) +
  shade_p_value(obs_stat = sleep_mean$mean_sleep_total, direction = "both")

p_val_mean <- null_distribution_mean %>% 
  get_p_value(obs_stat = sleep_mean$mean_sleep_total, direction = "both")

p_val_mean
```

> the p value is >0.0001 and therefore there is evidence to reject the null hypothesis


## Q3
### Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

H0: the mean total_sleep for omnivores and the mean total_sleep for herbivores is the same 
H1: the mean total_sleep for omnivores is greater than (>) the mean total_sleep for herbivores 
sig = 0.05

Two-sample mean hypothesis test (independent)

```{r}
null_dist_vore <- msleep %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 5000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```
 > I can't get infer to work 
 > I'm not seeing what the issue is
 > Error keeps being thrown no matter what stat I chose
 
 
 ## Question 4
 ### Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%
 
 H0: the proportion of domesticated animals is 5%
 H1: the proportion of domesticated animals is greater than 5%
 sig = 0.05

One-sample proportion 
```{r}
msleep <- msleep %>% 
  mutate(is_domesticated = case_when(
    conservation == "domesticated" ~ TRUE,
    TRUE ~ FALSE
  ))

# assumption: I've imputed all NAs to be non-domesticated
```

```{r}
observed_prop <- msleep %>% 
  summarise(prop_domesticated = mean(is_domesticated))

observed_prop
```
```{r}
null_dist_prop <- msleep %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "draw") %>% 
  calculate(stat = "prop")

null_dist_prop %>% 
  visualise() +
  shade_p_value(obs_stat = observed_prop$prop_domesticated, direction = "right")

p_val_prop <- null_dist_prop %>% 
  get_p_value(obs_stat = observed_prop$prop_domesticated, direction = "right")

p_val_prop
```


> p value is less than 0.05 therefore we can reject the null hypothesis. There is evidence to suggest that the proportion of domesticated animals is greater than 5%


# 1.2 Defining the hypothesis

## Q1
### Coffee shop

H0: 
- the proportion of the town that have heard of the coffee shop is 40%
- $pi$ = 40%
H1:
- the proportion of the town that have heard of the coffee shop is greater than 40%
- $pi$ > 40%

Method:
- one-sample proportion 
- "draw"/ simulation

## Q2
### A/B test

H0:
- the proportion of customers that clicked through was the same for both A and B
- p1 - p2 = 0
H1:
- the proportion of customers that clicked through was higher for B than A
- p2 > p1

Method:
- two-sample proportion
- permute

# Q3
### Manufacturing

H0: 
- the width of the parts is 145mm
- $mu$ = 145mm
H1:
- the width of the parts is not 145mm
- $mu$ ≠ 154mm

# 1.3

# Q1
## Coffee shop

> p-value is more than 0.05 therefore we cannot reject the null hypothesis

# Q2
## A/B test

> p-value is less than threshold, therefore we reject the null hypothesis. 
> There is evidence to suggest that a higher proportion of customers in group B clicked through

## Q3
### Manufactoring

> The p-value is higher that the significance level therefore we fail to reject the null hypothesis



