---
title: "R Notebook"
output: html_notebook
---
# Week 1 Weekend HMWK 


## Load in tidyverse and the data
```{r}
library(tidyverse)
```

```{r}
books <- read_csv("data/books.csv")
```

## Explore the data

```{r}
dim(books)
```

```{r}
glimpse(books)
```

```{r}
view(books)
```

## Check for NAs

```{r}
sum(is.na(books))
```

## Slack Questions

### 1. What five books have the highest 'average_rating'?

```{r}
books %>% 
  select(title, authors, average_rating) %>% 
  slice_max(average_rating, n = 5)

# Setting wit_ties to FALSE for strict top 5
books %>% 
  select(title, authors, average_rating) %>% 
  slice_max(average_rating, n = 5, with_ties = FALSE)
```

### 2. Which book has the most 'text_reviews'?

```{r}
books %>% 
  select(title, authors, text_reviews_count) %>% 
  slice_max(text_reviews_count, n = 1)
```

### 3. Which book has the most ratings?

```{r}
books %>% 
  select(title, authors, ratings_count) %>% 
  slice_max(ratings_count, n = 1)
```

### 4. Which publisher has the highest 'average_rating'?

```{r}
books %>% 
  select(publisher, average_rating) %>% 
  slice_max(average_rating, n = 1, with_ties = FALSE)
```

### 5. How many pages is the longest book for each 'language_code'?

```{r}
books %>% 
  select(num_pages, language_code) %>% 
  group_by(language_code) %>% 
  slice_max(num_pages, n = 1)

# Checking how many distinct language_codes there are
books %>% 
  distinct(language_code)

# Setting with_ties to FALSE as there are repeated values
books %>% 
  select(num_pages, language_code) %>% 
  group_by(language_code) %>% 
  slice_max(num_pages, n = 1, with_ties = FALSE)
```

### 6. What is the highest rated book for each 'language_code'?

```{r}
books %>% 
  select(title, authors, average_rating, language_code) %>% 
  group_by(language_code) %>% 
  slice_max(average_rating, n = 1)

# With_ties = FALSE
books %>% 
  select(title, authors, average_rating, language_code) %>% 
  group_by(language_code) %>% 
  slice_max(average_rating, n = 1, with_ties = FALSE)
```



## My Questions

### 1. How many books has each publisher published?

```{r}
books %>% 
  distinct(publisher)
```


```{r}
books %>% 
  group_by(publisher) %>% 
  summarise(publisher, no_of_books = n()) %>% 
  arrange(desc(no_of_books))

# Got a bit lost on how to filter the results so that there isn't a row for each intance of publisher name 
```

### 2. Create subset of the data for books published by vintage

```{r}
vintage_books <- books %>% 
  filter(publisher == "Vintage")

vintage_books
```

### 3. Which authors has Vintage published? Arrange them alphabetically. 

```{r}
vintage_books %>% 
  distinct(authors) %>% 
  arrange(authors)
```

### 4. Which languages does Vintage publish in?

```{r}
vintage_books %>% 
  group_by(language_code) %>% 
  summarise(no_of_lang_books = n())
```

### 5. What is the one 'spa' (Spanish?) book Vintage has published?

```{r}
vintage_books %>% 
  filter(language_code == "spa") %>% 
  select(title, authors)
```

### 6. What is the average number of pages of books published by Vintage? Save it to a vector called 'avg_num_pages' and round to the nearest whole number.

```{r}
avg_num_pages <- vintage_books %>%
  summarise(avg_num_pages = round(mean(num_pages), digits = 0)) %>%
  pull()

avg_num_pages
```

### 7. Create a column called "diff_from_avg" that takes num_pages per book away from the "avg_num_pages".

```{r}
vintage_books %>% 
  mutate(diff_from_avg = num_pages - avg_num_pages, .after = num_pages)

# New column could have a better name
```


### 8. What is the shortest book published? What is the longest book published?

```{r}
vintage_books %>% 
  select(title, authors, num_pages) %>% 
  slice_min(num_pages)
```

```{r}
vintage_books %>% 
  select(title, authors, num_pages) %>% 
  slice_max(num_pages)
```

### 9. Create a new column called 'diff_rating_review' that calculates the difference between the number of ratings and the number of text reviews a book recieved. 

```{r}
vintage_books %>% 
  mutate(diff_rating_review = ratings_count - text_reviews_count, .after = text_reviews_count)
```

